Mapping plant-pollinator interactions across Europe

### 2024-01-04 Manuscript/Ms.qmd
Relatively large update (Manincor, Fisogni and Petanidou added)

```{r echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE}
#Print number of countries
data = readRDS("../Data/Interactions_uncounted.rds")
#Country number
country_number = data %>% 
select(Country) %>% 
n_distinct()
#Study number
study_number = data %>% 
select(Study_id) %>% 
n_distinct()
#Minimum year
min_year = data %>% 
select(Year) %>% 
slice(which.min(Year)) %>% 
pull()
#Maximum year
max_year = data %>% 
select(Year) %>% 
slice(which.max(Year)) %>% 
pull()
#Number of interactions
interaction_number = nrow(data)
#Check number of accepted pollinators
pollinator_spp_number = data %>% 
select(Pollinator_rank, Pollinator_accepted_name)%>%
filter(Pollinator_rank == "SPECIES") %>% 
select(Pollinator_accepted_name) %>% 
n_distinct()
#Check number of plant species
plant_spp_number = data %>% 
select(Plant_rank, Plant_status, 
Plant_matchtype, Plant_accepted_name) %>% 
filter(Plant_rank == "SPECIES") %>% 
select(Plant_accepted_name) %>% 
n_distinct()

@@

This European metaweb consist of datasets of plant-pollinator interactions compiled initially by a wide number of researchers and institutions within the European continent. This dataset covers `r country_number` countries and consist of `r study_number` independent published and unpublished studies conducted during the time period `r min_year` - `r max_year`, and accounts for a total of `r prettyNum(interaction_number, big.mark=",")` interactions from `r prettyNum(pollinator_spp_number, big.mark=",")` pollinator and `r prettyNum(plant_spp_number, big.mark=",")` plant species.

>>>>

```{r echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE}
#Print number of countries
data = readRDS("../Data/Interactions_uncounted.rds")
#Country number
country_number = data %>% 
select(Country) %>% 
n_distinct()
#Study number
study_number = data %>% 
select(Study_id) %>% 
n_distinct()
#Average study number
studies_by_country = data %>% 
group_by(Country) %>% 
summarise(study_number = n_distinct(Study_id)) %>% 
summarise(mean(study_number)) %>% 
pull()
#$\bar{x}_\frac{studies}{country}$ = `r studies_by_country`
#Sampling method
Sampling_method = data %>% 
group_by(Study_id) %>% 
distinct(Sampling_method) %>%  
ungroup() %>% 
count(Sampling_method) %>% 
mutate(percent_method = n/sum(n) *100) %>% 
mutate(Sampling_method = recode_factor(Sampling_method, "Transect" = "transects"))
#1st most common sampling methodology
most_common_method = Sampling_method %>% 
filter(percent_method == max(percent_method)) 
#Minimum year
min_year = data %>% 
select(Year) %>% 
slice(which.min(Year)) %>% 
pull()
#Maximum year
max_year = data %>% 
select(Year) %>% 
slice(which.max(Year)) %>% 
pull()
#Number of interactions
interaction_number = nrow(data)
#Check number of accepted pollinators
pollinator_spp_number = data %>% 
select(Pollinator_rank, Pollinator_accepted_name)%>%
filter(Pollinator_rank == "SPECIES") %>% 
select(Pollinator_accepted_name) %>% 
n_distinct()
#Check number of plant species
plant_spp_number = data %>% 
select(Plant_rank, Plant_status, 
Plant_matchtype, Plant_accepted_name) %>% 
filter(Plant_rank == "SPECIES") %>% 
select(Plant_accepted_name) %>% 
n_distinct()

@@

This European metaweb consist of datasets of plant-pollinator interactions compiled initially by a wide number of researchers and institutions within the European continent. This dataset consist of `r study_number` independent published and unpublished studies conducted during the time period `r min_year` - `r max_year` on `r country_number` different countries (**Figure 1a**). The dataset contains a total of `r prettyNum(interaction_number, big.mark=",")` distinct interactions, considering interaction as the contact of a given pollinator to the reproductive structure of a particular plant, from `r prettyNum(pollinator_spp_number, big.mark=",")` pollinator and `r prettyNum(plant_spp_number, big.mark=",")` plant species. These different studies differ in sampling effort and methodology, although most studies took place within a single flowering season (PERCENTAGE) with an average of XXX sampling days (range XXX to XXXX) over a time span of XXXX days, and documented interactions mostly by using `r  most_common_method[[1]]` (`r  most_common_method[[3]]`%).

Explain % of taxonomic ranks at order level that constitute the included pollinators. Something with the different pollinators is going to be graph 2.
